Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-28 paper.tex
Add declarations

>>>>

\section{Declarations}
\subsection{Availability of data and materials}

The datasets analysed during the study are available in the corresponding databases or repositories \parencite{ChairOfEconometricsAndStatisticsAtKarlsruheInstituteOfTechnology2024,Rostami-Tabar2023, Moody2017}.
All code is available in the repository [GITHUB LINK WILL BE PROVIDED AFTER REVIEW].

\subsection{Competing interests}
The authors declare that they have no competing interests.

\subsection{Funding}

JR greatfully acknowledges funding by the Bischoefliche Studienstiftung Cusanuswerk (Bonn, Germany).

\subsection{Authors' contributions}

OG, BL and JR developed the theoretical formalism.
BL and JR implemented the methods.
JR conducted the simulations and analyzed the data.
BL and JR wrote the manuscript.
All authors discussed the results, critically reviewed and contributed to the final manuscript.

\subsection{Acknowledgments}

Not applicable.
